Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2023-08-29 manuscript/manuscript.tex
Added gisttools import to codeblock
Added matplotlib to list of required python packages

Furthermore, a recent Python version (3.6 or newer) should be available with the following packages installed:
\begin{itemize}
	\item \software{gisttools} (\url{https://github.com/liedllab/gisttools}, $\geq$ 0.2)
	\item \software{mdtraj} (\url{https://www.mdtraj.org/}, $\geq$ 1.9.7) \cite{McGibbon2015-mdtraj}
\end{itemize}

@@

\begin{lstlisting}[style=python]
def select(traj, sel):
	# Slice a Trajectory by selection mask.
	return traj.atom_slice(traj.top.select(sel))
### Load GIST data
compl = gt.gist.load_gist_file(
	'complex/gist/gistoutlong.dat', 
	struct='complex/gist/gist_nowat.pdb')
### Define ligand atoms and find voxels around them
rmax = 3.5
biotin_mask = 'resname BTN and not element H'
btn = select(compl.struct, biotin_mask).xyz[0] * 10.
ind, _, _ = compl.distance_to_spheres(btn, rmax)

>>>>

Furthermore, a recent Python version (3.6 or newer) should be available with the following packages installed:
\begin{itemize}
	\item \software{gisttools} (\url{https://github.com/liedllab/gisttools}, $\geq$ 0.2)
	\item \software{mdtraj} (\url{https://www.mdtraj.org/}, $\geq$ 1.9.7) \cite{McGibbon2015-mdtraj}
	\item \software{matplotlib} (\url{https://matplotlib.org/}, $\geq$ 3.7.0) \cite{Hunter2007-matplotlib}
\end{itemize}

@@

\begin{lstlisting}[style=python]
import gisttools as gt
def select(traj, sel):
	# Slice a Trajectory by selection mask.
	return traj.atom_slice(traj.top.select(sel))
### Load GIST data
compl = gt.gist.load_gist_file(
	'complex/gist/gistoutlong.dat', 
	struct='complex/gist/gist_nowat.pdb')
### Define ligand atoms and find voxels around them
rmax = 3.5
biotin_mask = 'resname BTN and not element H'
btn = select(compl.struct, biotin_mask).xyz[0] * 10.
ind, _, _ = compl.distance_to_spheres(btn, rmax)
